---
title: 'M1 EDEN Thesis: Main Results + ADHD'
author: "Victoria Shevchenko"
date: "06/05/2022"
output:
  html_document:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, 
                      results="asis",
                      #out.extra = 'style="display:block; margin: auto"',
                      fig.align = "center", dpi=200)

library(tidybayes)
library(tidyr)
library(purrr)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(kableExtra)
library(scales)
library(Hmisc)
library(data.table)
library(gtools)


theme_set(theme_bw())
```

# Correlation Tables

ADHD variables:

  * 5 years: hyp5
  * 11 years, CBCL: CBCLVI
  * 11 years, SDQ: SDQHYP
  * 11 years, MIA:(IMP[impulsivité] + INA[inattention] + HYP[hyperactivité]) / 3

```{r, include =F}
cortable_5 <-function(x, removeTriangle=c("upper", "lower"),
                      result=c("none", "html", "latex")) { 
  x <- as.matrix(x)
  correlation_matrix<-rcorr(x, type = "spearman")
  R <- correlation_matrix$r 
  p <- correlation_matrix$P  
  
  mystars <- ifelse(p < .0025, "***", ifelse(p < .0125, "** ", ifelse(p < .05, "*  ", ifelse(p < .05, "*   ", "    "))))
  
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
  
  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
  diag(Rnew) <- paste(diag(R), " ", sep="")
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep="")
  
  if(removeTriangle[1]=="upper"){
    Rnew <- as.matrix(Rnew)
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew)
  }
  
  else if(removeTriangle[1]=="lower"){
    Rnew <- as.matrix(Rnew)
    Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew)
  }
  Rnew <- cbind(Rnew[6:ncol(x),1:5])
  if (result[1]=="none") return(Rnew)
  else{
    if(result[1]=="html") print(xtable(Rnew), type="html")
    else print(xtable(Rnew), type="latex") 
  }
}

# For 11 years
cortable_11 <-function(x, removeTriangle=c("upper", "lower"),
                    result=c("none", "html", "latex")) { 
  x <- as.matrix(x)
  correlation_matrix<-rcorr(x, type = "spearman")
  R <- correlation_matrix$r 
  p <- correlation_matrix$P  
  
  mystars <- ifelse(p < .0008, "***", ifelse(p < .004, "** ", ifelse(p < .05, "*  ", ifelse(p < .05, "*   ", "    "))))
  
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]

  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
  diag(Rnew) <- paste(diag(R), " ", sep="")
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep="")
  
  if(removeTriangle[1]=="upper"){
    Rnew <- as.matrix(Rnew)
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew)
  }
  
  else if(removeTriangle[1]=="lower"){
    Rnew <- as.matrix(Rnew)
    Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew)
  }
  Rnew <- cbind(Rnew[6:ncol(x),1:5])
  if (result[1]=="none") return(Rnew)
  else{
    if(result[1]=="html") print(xtable(Rnew), type="html")
    else print(xtable(Rnew), type="latex") 
  }
}

```

```{r, include = F}
setwd(getwd())
load("participants_5.Rdata")
load("participants_11_CBCL.Rdata")
load("participants_11_SDQ.Rdata")
load("participants_11_MIA.Rdata")
```

```{r, include = F}
correlation_vars_5 <- subset(participants_5, select = c("Full-Scale IQ", 
                                                        "Verbal IQ", 
                                                        "Performance IQ",
                                                        "|VIQ-PIQ|", 
                                                        "VIQ-PIQ",
                                                        "Internalizing Disorder",
                                                        "Conduct Disorder", 
                                                        "Social Problems",
                                                        "ADHD"))

correlation_vars_11_CBCL <- subset(participants_11_CBCL, select = c("Full-Scale IQ", 
                                                                    "Verbal IQ", 
                                                                    "Performance IQ",
                                                                    "|VIQ-PIQ|", 
                                                                    "VIQ-PIQ",
                                                                    "Internalizing Disorder, CBCL",
                                                                    "Conduct Disorder, CBCL", 
                                                                    "Social Problems, CBCL",
                                                                    "ADHD, CBCL"))

correlation_vars_11_SDQ <- subset(participants_11_SDQ, select = c("Full-Scale IQ", 
                                                                  "Verbal IQ", 
                                                                  "Performance IQ",
                                                                  "|VIQ-PIQ|", 
                                                                  "VIQ-PIQ",
                                                                  "Internalizing Disorder, SDQ",
                                                                  "Conduct Disorder, SDQ", 
                                                                  "Social Problems, SDQ",
                                                                  "ADHD, SDQ"))

correlation_vars_11_MIA <- subset(participants_11_MIA, select = c("Full-Scale IQ", 
                                                                  "Verbal IQ", 
                                                                  "Performance IQ",
                                                                  "|VIQ-PIQ|", 
                                                                  "VIQ-PIQ",
                                                                  "Internalizing Disorder, MIA",
                                                                  "Conduct Disorder, MIA", 
                                                                  "Social Problems, MIA",
                                                                  "ADHD, MIA"))
```

```{r, echo = F}
correlation_table_5 <- cortable_5(correlation_vars_5)
correlation_table_11_CBCL <- cortable_11(correlation_vars_11_CBCL)
correlation_table_11_SDQ <- cortable_11(correlation_vars_11_SDQ)
correlation_table_11_MIA <- cortable_11(correlation_vars_11_MIA)
```

```{r cor-matrix-all, output = 'asis', results = "hold", out.height = '100%', out.width = '100%', fig.align = "center", echo = F}
cor_matrix_data_5y = subset(participants_5, select = c("ID","Full-Scale IQ", 
                                                        "Verbal IQ", 
                                                        "Performance IQ",
                                                        "|VIQ-PIQ|", 
                                                        "VIQ-PIQ"))

cor_matrix_data_11y = subset(participants_11_SDQ, select = c("ID","Full-Scale IQ", 
                                                        "Verbal IQ", 
                                                        "Performance IQ",
                                                        "|VIQ-PIQ|", 
                                                        "VIQ-PIQ"))

```

```{r, output = 'asis', results = "hold", out.height = '100%', out.width = '100%', fig.align = "center", echo = F}
cor_matrix_data_5y <- cor_matrix_data_5y %>%
  rename("FSIQ, 5y" = "Full-Scale IQ",
         "VIQ, 5y" = "Verbal IQ",
         "PIQ, 5y" = "Performance IQ",
         "|VIQ-PIQ|, 5y" = "|VIQ-PIQ|",
         "VIQ-PIQ, 5y" = "VIQ-PIQ")

cor_matrix_data_11y <- cor_matrix_data_11y %>%
  rename("FSIQ, 11y" = "Full-Scale IQ",
         "VIQ, 11y" = "Verbal IQ",
         "PIQ, 11y" = "Performance IQ",
         "|VIQ-PIQ|, 11y" = "|VIQ-PIQ|",
         "VIQ-PIQ, 11y" = "VIQ-PIQ")

cor_both_ages = merge(cor_matrix_data_5y, cor_matrix_data_11y, by = "ID")
cor_both_ages = select(cor_both_ages, -"ID")
cor_matrix_both_ages = cor(cor_both_ages, method = c("spearman"))[1:5, 6:10]
pval_cor_matrix_both_ages<- psych::corr.test(cor_both_ages, method = "spearman")$p[1:5, 6:10]
corrplot::corrplot(cor_matrix_both_ages, method = "square", type = "upper", addCoef.col = 'black', p.mat = pval_cor_matrix_both_ages, insig = "blank", sig.level = 0.05, tl.col = "black", tl.srt = 45, title = "Index correlations across ages", mar=c(0,0,3,0)) +
  theme(text = element_text(size = 18))
```

```{r, output = 'asis', results = "hold", out.height = '100%', out.width = '100%', fig.align = "center", echo = F}
cor_matrix_data_5y <- cor_matrix_data_5y %>%
  rename("FSIQ" = "FSIQ, 5y",
         "VIQ" = "VIQ, 5y",
         "PIQ" = "PIQ, 5y",
         "|VIQ-PIQ|" = "|VIQ-PIQ|, 5y",
         "VIQ-PIQ" = "VIQ-PIQ, 5y")

cor_matrix_data_11y <- cor_matrix_data_11y %>%
  rename("FSIQ" = "FSIQ, 11y",
         "VIQ" = "VIQ, 11y",
         "PIQ" = "PIQ, 11y",
         "|VIQ-PIQ|" = "|VIQ-PIQ|, 11y",
         "VIQ-PIQ" = "VIQ-PIQ, 11y")

cor_matrix_data_5y = select(cor_matrix_data_5y, -"ID")
cor_matrix_data_11y = select(cor_matrix_data_11y, -"ID")

cor_matrix_5 <- cor(cor_matrix_data_5y, method = c("spearman"))
cor_matrix_11 <- cor(cor_matrix_data_11y, method = c("spearman"))

pval_cor_matrix_5 <- psych::corr.test(cor_matrix_data_5y, method = "spearman")$p
pval_cor_matrix_11 <- psych::corr.test(cor_matrix_data_11y, method = "spearman")$p

corrplot::corrplot(cor_matrix_5, method = "square", type = "upper", addCoef.col = 'black', p.mat = pval_cor_matrix_5, insig = "blank", sig.level = 0.05, tl.col = "black", diag = FALSE, mar=c(0,0,4,0),  tl.srt = 45, title = "Inter-index correlations at 5.5 years") +
  theme(text = element_text(size = 18))
```


```{r, output = 'asis', results = "hold", out.height = '100%', out.width = '100%', fig.align = "center", echo = F}

corrplot::corrplot(cor_matrix_11, method = "square", type = "upper", addCoef.col = 'black', p.mat = pval_cor_matrix_11, insig = "blank", sig.level = 0.05, tl.col = "black", diag = FALSE, mar=c(0,0,3,0),  tl.srt = 45, title = "Inter-index correlations at 11.5 years") +
  theme(text = element_text(size = 18))

```

```{r, output = 'asis', echo = F, fig.show = "hold", out.width="120%",out.height="120%"}
alignment= map_chr(correlation_table_5, ~ifelse(class(.x)=="numeric", "r","l"))

correlation_table_5 %>% 
  kbl(caption="Spearman's correlations: 5-year-olds", align=alignment) %>% 
  kable_classic(full_width=TRUE, html_font="Times")
```

```{r, output = 'asis', echo = F, fig.show = "hold", out.width="120%",out.height="120%"}
alignment= map_chr(correlation_table_11_CBCL, ~ifelse(class(.x)=="numeric", "r","l"))

correlation_table_11_CBCL %>% 
  kbl(caption="Spearman's correlations: 11 years, CBCL", align=alignment) %>% 
  kable_classic(full_width=TRUE, html_font="Times")
```

```{r, output = 'asis', echo = F, fig.show = "hold", out.width="120%",out.height="120%"}
alignment= map_chr(correlation_table_11_SDQ, ~ifelse(class(.x)=="numeric", "r","l"))

correlation_table_11_SDQ %>% 
  kbl(caption="Spearman's correlations: 11 years, SDQ", align=alignment) %>% 
  kable_classic(full_width=TRUE, html_font="Times")
```

```{r, output = 'asis', echo = F, fig.show = "hold", out.width="120%",out.height="120%"}
alignment= map_chr(correlation_table_11_MIA, ~ifelse(class(.x)=="numeric", "r","l"))

correlation_table_11_MIA %>% 
  kbl(caption="Spearman's correlations: 11 years, MIA", align=alignment) %>% 
  kable_classic(full_width=TRUE, html_font="Times")
```

# Quintiles

```{r, include = F}
# 5 YEARS
long_participants_5 <- reshape(participants_5,
                               direction = "long",
                               idvar = c("ID", "Sex", "Age"),
                               varying = c("Full-Scale IQ", 
                                           "Verbal IQ",
                                           "Performance IQ",
                                           "|VIQ-PIQ|", 
                                           "VIQ-PIQ"),
                               v.names = "Cognitive Score",
                               timevar = "Cognitive Measure",
                               times = c("Full-Scale IQ", 
                                         "Verbal IQ",
                                         "Performance IQ",
                                         "|VIQ-PIQ|", 
                                         "VIQ-PIQ"))

long_participants_5 <- reshape(long_participants_5,
                               direction = "long",
                               idvar = c("ID", 
                                         "Sex",
                                         "Age", 
                                         "Cognitive Measure", 
                                         "Cognitive Score"),
                               varying = c("Conduct Disorder", 
                                           "Internalizing Disorder", 
                                           "Social Problems",
                                           "ADHD"),
                               v.names = "Psychopathology Score",
                               timevar = "Psychopathology Measure",
                               times = c("Conduct Disorder", 
                                         "Internalizing Disorder", 
                                         "Social Problems",
                                         "ADHD"))

long_participants_5$`Cognitive Measure` <- as.factor(long_participants_5$`Cognitive Measure`)
long_participants_5$`Psychopathology Measure` <- as.factor(long_participants_5$`Psychopathology Measure`)
long_participants_5$`Cognitive Measure` <- factor(long_participants_5$`Cognitive Measure`, 
                                                  levels = c("Full-Scale IQ", 
                                                            "Verbal IQ",
                                                            "Performance IQ",
                                                            "|VIQ-PIQ|", 
                                                            "VIQ-PIQ"))

long_participants_5$`Psychopathology Measure` <- factor(long_participants_5$`Psychopathology Measure`,
                                                        levels = c("Internalizing Disorder", 
                                                                   "Conduct Disorder",
                                                                   "Social Problems",
                                                                   "ADHD"))
```

```{r, include = F}
# 11 YEARS

long_participants_11_CBCL <- reshape(participants_11_CBCL,
                                     direction = "long",
                                     idvar = c("ID", "Sex", "Age"),
                                     varying = c("Full-Scale IQ", 
                                                 "Verbal IQ",
                                                 "Performance IQ",
                                                 "|VIQ-PIQ|", 
                                                 "VIQ-PIQ"),
                                     v.names = "Cognitive Score",
                                     timevar = "Cognitive Measure",
                                     times = c("Full-Scale IQ", 
                                               "Verbal IQ",
                                               "Performance IQ",
                                               "|VIQ-PIQ|", 
                                               "VIQ-PIQ"))

long_participants_11_CBCL <- reshape(long_participants_11_CBCL,
                                     direction = "long",
                                     idvar = c("ID", "Sex", "Age", "Cognitive Score", "Cognitive Measure"),
                                     varying = c("Internalizing Disorder, CBCL", 
                                                 "Conduct Disorder, CBCL",
                                                 "Social Problems, CBCL",
                                                 "ADHD, CBCL"),
                                     v.names = "Psychopathology Score",
                                     timevar = "Psychopathology Measure",
                                     times = c("Internalizing Disorder, CBCL", 
                                               "Conduct Disorder, CBCL",
                                               "Social Problems, CBCL",
                                               "ADHD, CBCL")) 

long_participants_11_CBCL$`Cognitive Measure` <- as.factor(long_participants_11_CBCL$`Cognitive Measure`)
long_participants_11_CBCL$`Cognitive Measure` <- factor(long_participants_11_CBCL$`Cognitive Measure`, levels = c("Full-Scale IQ", 
                                                                                                                "Verbal IQ",
                                                                                                                "Performance IQ",
                                                                                                                "|VIQ-PIQ|", 
                                                                                                                "VIQ-PIQ"))
long_participants_11_CBCL$`Psychopathology Measure` <- as.factor(long_participants_11_CBCL$`Psychopathology Measure`)
long_participants_11_CBCL$`Psychopathology Measure` <- factor(long_participants_11_CBCL$`Psychopathology Measure`, levels = c("Internalizing Disorder, CBCL", 
                                                                                                                  "Conduct Disorder, CBCL",
                                                                                                                  "Social Problems, CBCL",
                                                                                                                  "ADHD, CBCL"))

```

```{r, include = F}
# SDQ
long_participants_11_SDQ <- reshape(participants_11_SDQ,
                                    direction = "long",
                                    idvar = c("ID", "Sex", "Age"),
                                    varying = c("Full-Scale IQ", 
                                                "Verbal IQ",
                                                "Performance IQ",
                                                "|VIQ-PIQ|", 
                                                "VIQ-PIQ"),
                                    v.names = "Cognitive Score",
                                    timevar = "Cognitive Measure",
                                    times = c("Full-Scale IQ", 
                                              "Verbal IQ",
                                              "Performance IQ",
                                              "|VIQ-PIQ|", 
                                              "VIQ-PIQ"))

long_participants_11_SDQ <- reshape(long_participants_11_SDQ,
                                    direction = "long",
                                    idvar = c("ID", "Sex", "Age", "Cognitive Score", "Cognitive Measure"),
                                    varying = c("Internalizing Disorder, SDQ", 
                                                "Conduct Disorder, SDQ",
                                                "Social Problems, SDQ",
                                                "ADHD, SDQ"),
                                    v.names = "Psychopathology Score",
                                    timevar = "Psychopathology Measure",
                                    times = c("Internalizing Disorder, SDQ", 
                                              "Conduct Disorder, SDQ",
                                              "Social Problems, SDQ",
                                              "ADHD, SDQ")) 

long_participants_11_SDQ$`Psychopathology Measure` <- as.factor(long_participants_11_SDQ$`Psychopathology Measure`)
long_participants_11_SDQ$`Cognitive Measure` <- as.factor(long_participants_11_SDQ$`Cognitive Measure`)
long_participants_11_SDQ$`Cognitive Measure` <- factor(long_participants_11_SDQ$`Cognitive Measure`, levels = c("Full-Scale IQ", 
                                                                "Verbal IQ",
                                                                "Performance IQ",
                                                                "|VIQ-PIQ|", 
                                                                "VIQ-PIQ"))
long_participants_11_SDQ$`Psychopathology Measure` <- factor(long_participants_11_SDQ$`Psychopathology Measure`,
                                                        levels = c("Internalizing Disorder, SDQ", 
                                                                   "Conduct Disorder, SDQ",
                                                                   "Social Problems, SDQ",
                                                                   "ADHD, SDQ"))
```

```{r, include = F}
long_participants_11_MIA <- reshape(participants_11_MIA,
                                    direction = "long",
                                    idvar = c("ID", "Sex", "Age"),
                                    varying = c("Full-Scale IQ", 
                                                "Verbal IQ",
                                                "Performance IQ",
                                                "|VIQ-PIQ|", 
                                                "VIQ-PIQ"),
                                    v.names = "Cognitive Score",
                                    timevar = "Cognitive Measure",
                                    times = c("Full-Scale IQ", 
                                              "Verbal IQ",
                                              "Performance IQ",
                                              "|VIQ-PIQ|", 
                                              "VIQ-PIQ"))

long_participants_11_MIA <- reshape(long_participants_11_MIA,
                                    direction = "long",
                                    idvar = c("ID", "Sex", "Age", "Cognitive Score", "Cognitive Measure"),
                                    varying = c("Internalizing Disorder, MIA", 
                                                "Conduct Disorder, MIA",
                                                "Social Problems, MIA",
                                                "ADHD, MIA"),
                                    v.names = "Psychopathology Score",
                                    timevar = "Psychopathology Measure",
                                    times = c("Internalizing Disorder, MIA", 
                                              "Conduct Disorder, MIA",
                                              "Social Problems, MIA",
                                              "ADHD, MIA")) 

long_participants_11_MIA$`Cognitive Measure` <- as.factor(long_participants_11_MIA$`Cognitive Measure`)
long_participants_11_MIA$`Psychopathology Measure` <- as.factor(long_participants_11_MIA$`Psychopathology Measure`)
long_participants_11_MIA$`Cognitive Measure` <- factor(long_participants_11_MIA$`Cognitive Measure`, levels = c("Full-Scale IQ", 
                                                                                                                "Verbal IQ",
                                                                                                                "Performance IQ",
                                                                                                                "|VIQ-PIQ|", 
                                                                                                                "VIQ-PIQ"))
long_participants_11_MIA$`Psychopathology Measure` <- factor(long_participants_11_MIA$`Psychopathology Measure`, levels = c("Internalizing Disorder, MIA", 
                                                                                                                "Conduct Disorder, MIA",
                                                                                                                "Social Problems, MIA",
                                                                                                                "ADHD, MIA"))
```

```{r, include = F}
# Data division in IQ quintiles
setDT(long_participants_5)[ , `Quintile` := quantcut(`Cognitive Score`, q = 5), by = `Cognitive Measure`]

long_participants_5 <- long_participants_5 %>%
  mutate(Quintile = factor(Quintile, levels = c("[-40,-4]", "(-4,4]", "[0,4]","(4,8]", "(4,10]", "(8,13]","(13,20]", "(10,19]", "(19,54]", "(20,54]", "[41,94]", "[44,97]", "[48,90]", "(90,96]", "(94,101]",  "(101,107]", "(96,103]","(97,103]", "(107,114]", "(103,111]", "(111,144]", "(111,118]", "(114,142]", "(118,147]")))

long_participants_11_CBCL[ , `Cognitive Score` := floor(`Cognitive Score`)] # Rounding down the IQ scores to remove decimals in the x-axis
long_participants_11_CBCL[ , Quintile := quantcut(`Cognitive Score`, q = 5), by = `Cognitive Measure`] # Adding quintiles

long_participants_11_SDQ[ , `Cognitive Score` := floor(`Cognitive Score`)] # Rounding down the IQ scores to remove decimals in the x-axis
long_participants_11_SDQ[ , Quintile := quantcut(`Cognitive Score`, q = 5), by = `Cognitive Measure`] # Adding quintiles

long_participants_11_MIA[ , `Cognitive Score` := floor(`Cognitive Score`)] # Rounding down the IQ scores to remove decimals in the x-axis
long_participants_11_MIA[ , Quintile := quantcut(`Cognitive Score`, q = 5), by = `Cognitive Measure`] # Adding quintiles

long_participants_11_MIA <- long_participants_11_MIA %>%
  mutate(Quintile = factor(Quintile, levels = c("[48,88]",  "[50,88]", "(88,97]",  "(97,104]", "(104,112]", "(112,131]", "[45,88]", "(88,98]", "(98,105]", "(105,112]", "(112,129]", "(104,113]", "(113,133]", "[0,2]", "(2,4]", "(4,7]", "(7,11]", "(11,36]", "[-37,-8]", "(-8,-3]", "(-3,1]", "(1,7]", "(7,26]")))

```


### 5 YEARS: Mean Score ± 2SE (y) vs. IQ quintiles (x)

```{r, fig.width=12, fig.height = 6, echo = F}
long_participants_5 %>% # In Performance IQ facet two X labels are permuted because of the deprecation of the duplicate (103,111] factor level
  ggplot(aes(x= `Quintile`, y =`Psychopathology Score`,  group = `Psychopathology Measure`, color=`Psychopathology Measure`)) + 
  geom_pointrange(stat="summary", fun.data=mean_se, fun.args = list(mult=2), position=position_dodge(0.05)) +
  geom_line(stat="summary", fun=mean) +
  facet_wrap(~`Cognitive Measure`, scales='free_x') +
  labs(x = "Quintiles", y ="Mean Score ± 2SE") +
  theme_bw()


```

### 11 YEARS, CBCL: Mean Score ± 2SE (y) vs. IQ quintiles (x)

```{r, fig.width=12, fig.height = 6, echo = F}
long_participants_11_CBCL %>% 
  ggplot(aes(x= `Quintile`, y =`Psychopathology Score`,  group = `Psychopathology Measure`, color=`Psychopathology Measure`)) + 
  geom_pointrange(stat="summary", fun.data=mean_se, fun.args = list(mult=2), position=position_dodge(0.05)) +
  geom_line(stat="summary", fun=mean) +
  facet_wrap(~`Cognitive Measure`, scales='free_x') +
  labs(x = "IQ Quintiles", y ="Mean Score ± 2SE") +
  theme_bw()
```

### 11 YEARS, SDQ: Mean Score ± 2SE (y) vs. IQ quintiles (x)

```{r, fig.width=12, fig.height = 6, echo = F}
long_participants_11_SDQ %>% 
  ggplot(aes(x= `Quintile`, y =`Psychopathology Score`,  group = `Psychopathology Measure`, color=`Psychopathology Measure`)) + 
  geom_pointrange(stat="summary", fun.data=mean_se, fun.args = list(mult=2), position=position_dodge(0.05)) +
  geom_line(stat="summary", fun=mean) +
  facet_wrap(~`Cognitive Measure`, scales='free_x') +
  labs(x = "IQ Quintiles", y ="Mean Score ± 2SE") +
  theme_bw()
```

### 11 YEARS, MIA: Mean Score ± 2SE (y) vs. IQ quintiles (x)

```{r, fig.width=12, fig.height = 6, echo = F}
long_participants_11_MIA %>% 
  ggplot(aes(x= `Quintile`, y =`Psychopathology Score`,  group = `Psychopathology Measure`, color=`Psychopathology Measure`)) + 
  geom_pointrange(stat="summary", fun.data=mean_se, fun.args = list(mult=2), position=position_dodge(0.05)) +
  geom_line(stat="summary", fun=mean) +
  facet_wrap(~`Cognitive Measure`, scales='free_x') +
  labs(x = "IQ Quintiles", y ="Mean Score ± 2SE") +
  theme_bw()
```


## Scatterplots

### 5 Years

```{r, out.width="80%",out.height="80%", echo = F}
plots_5_IQ_vs_psy = list()

for (Cognitive_Measure in levels(long_participants_5$`Cognitive Measure`)) {
  plots_5_IQ_vs_psy[[Cognitive_Measure]] = ggplot(long_participants_5 %>% filter(`Cognitive Measure` == Cognitive_Measure),
                                                  aes(x = `Cognitive Score`, y = `Psychopathology Score`, group = `Psychopathology Measure`)) +
    geom_point() + 
    geom_smooth(method='lm', color = "red", size = 1) +
    geom_count() +
    scale_size_area() +
    theme_bw() +
    labs(x = Cognitive_Measure) +
    facet_wrap(~ `Psychopathology Measure`)
  print(plots_5_IQ_vs_psy[[Cognitive_Measure]])
}

```

### 11.5 Years: CBCL

```{r, out.width="80%",out.height="80%", echo = F}

plots_11_IQ_vs_psy_CBCL  = list()

for (Cognitive_Measure in levels(long_participants_11_CBCL$`Cognitive Measure`)) {
  plots_11_IQ_vs_psy_CBCL[[Cognitive_Measure]] = ggplot(long_participants_11_CBCL %>% 
                                                          filter(`Cognitive Measure` == Cognitive_Measure),
                                                        aes(x = `Cognitive Score`, y = `Psychopathology Score`, group = `Psychopathology Measure`)) +
    geom_point() + 
    geom_smooth(method='lm', color = "red", size = 1) +
    theme_bw() +
    labs(x = Cognitive_Measure) +
    facet_wrap(~ `Psychopathology Measure`)
  print(plots_11_IQ_vs_psy_CBCL[[Cognitive_Measure]])
}

```

### 11.5 Years: SDQ

```{r, out.width="80%",out.height="80%", echo = F}

plots_11_IQ_vs_psy_SDQ  = list()

for (Cognitive_Measure in levels(long_participants_11_SDQ$`Cognitive Measure`)) {
  plots_11_IQ_vs_psy_SDQ[[Cognitive_Measure]] = ggplot(long_participants_11_SDQ %>% 
                                                         filter(`Cognitive Measure` == Cognitive_Measure),
                                                       aes(x = `Cognitive Score`, y = `Psychopathology Score`, group = `Psychopathology Measure`)) +
    geom_point() + 
    geom_smooth(method='lm', color = "red", size = 1) +
    theme_bw() +
    labs(x = Cognitive_Measure) +
    facet_wrap(~ `Psychopathology Measure`)
  print(plots_11_IQ_vs_psy_SDQ[[Cognitive_Measure]])
}

```

### 11.5 Years: MIA

```{r, out.width="80%",out.height="80%", echo = F}

plots_11_IQ_vs_psy_MIA  = list()

for (Cognitive_Measure in levels(long_participants_11_MIA$`Cognitive Measure`)) {
  plots_11_IQ_vs_psy_MIA[[Cognitive_Measure]] = ggplot(long_participants_11_MIA %>% 
                                                         filter(`Cognitive Measure` == Cognitive_Measure),
                                                       aes(x = `Cognitive Score`, y = `Psychopathology Score`, group = `Psychopathology Measure`)) +
    geom_point() + 
    geom_smooth(method='lm', color = "red", size = 1) +
    theme_bw() +
    labs(x = Cognitive_Measure) +
    facet_wrap(~ `Psychopathology Measure`)
  print(plots_11_IQ_vs_psy_MIA[[Cognitive_Measure]])
}

```



